Monitoring and predictive mapping of floristic biodiversity along a climatic gradient in ENSO's terrestrial core region, NW Peru

### 2020-08-11 docs/enso_comp.Rmd
put ms into docs and just keep necessary files

title: "Monitoring and predictive mapping of floristic biodiversity along a climatic gradient in ENSO's terrestrial core region, NW Peru"
bibliography: ../transect_refs.bib
csl: ../ecography.csl
# biblio-style: "natbib"
link-citations: true
---

>>>>

title: "Monitoring and predictive mapping of floristic biodiversity along a climatic gradient in ENSO's terrestrial core region, NW Peru"
bibliography: transect_refs.bib
csl: ecography.csl
# biblio-style: "natbib"
link-citations: true
---

### 2020-08-11 docs/title_page.Rmd
put ms into docs and just keep necessary files

title: "Monitoring and predictive mapping of floristic biodiversity along a climatic gradient in ENSO's terrestrial core region, NW Peru"
#bibliography: transect_refs.bib
#csl: ecography.csl
# biblio-style: "natbib"
#link-citations: true
---

>>>>

title: "Monitoring and predictive mapping of floristic biodiversity along a climatic gradient in ENSO's terrestrial core region, NW Peru"
bibliography: transect_refs.bib
csl: ecography.csl
# biblio-style: "natbib"
#link-citations: true
---
